TODO: A Survey of StarCraft AI Techniques

### 2013-02-03 survey.tex

% MACHINE LEARNING:
Concerning machine learning-based approaches, Weber and Mateas \cite{WeberCig09} proposed ``a data mining approach to strategy prediction'' and performed supervised learning (from buildings features) on labeled StarCraft replays. Dereszynski et al. \cite{HMMstrat_RTS_AIIDE11} used HMM to learn the transition probabilities of sequences of constructions and kept the most probables to produce probabilistic behavior models (in StarCraft). Synnaeve and Bessi\`{e}re \cite{SynnaeveOpeningCig11} used the dataset of \cite{WeberCig09} and presented a Bayesian semi-supervised model to learn from replays and predict openings (early game strategies) from StarCraft replays. The openings are labeled by EM clustering considering appropriate features. Then in \cite{SynnaeveAIIDE11}, they presented an unsupervised learning Bayesian model for tech-tree prediction, still using replays.

@@

% MACHINE LEARNING:
Concerning tactical decision making, many different approaches have been explored such as machine learning or game tree search. Concerning machine learning approaches, 
Hladky and Bulitko \cite{Hladky2008} benchmarked hidden semi-Markov models (HSMM) and particle filters in first person shooter games (FPS) units tracking. They showed that the accuracy of occupancy maps was improved using movement models (learned from the player behavior) in HSMM. Kabanza et al. \cite{OBRecog} improve the probabilistic hostile agent task tracker (PHATT \cite{PHATT}, a simulated HMM for plan recognition) by encoding strategies as HTN, used for plan and intent recognition to find tactical opportunities. Sharma et al. \cite{CBR-RL} combined CBR and reinforcement learning to enable reuse of tactical plan components. Finally, Cadena and Garrido \cite{CadenaG11} used fuzzy CBR (fuzzy case matching) for strategic and tactical planning.

@@

% Machine learning:
There has been a significant amount of work on using machine learning techniques for the problem of reactive control. Bayesian modeling has been applied to inverse fusion of the sensory inputs of the units \cite{SynnaeveMicroCig11}, which subsumes potential fields, allowing for integration of tactical goals directly in micro-management. 
Additionally, there has been some interesting uses of reinforcement learning (RL) \cite{Sutton}: Marthi et al. \cite{Marthi05} employ concurrent hierarchical Q-learning (units Q-functions are combined at the group level) RL to efficiently control units in a ``one robot with multiple effectors'' fashion. Madeira et al. \cite{Madeira06} advocate the use of prior domain knowledge to allow faster RL learning and applied their work on a turn-based strategy game. In real game setups, the actions spaces to explore is gigantic, it requires to use the structure of the game in a partial program (or a partial Markov decision process) and a shape function (or a heuristic) \cite{Marthi05}. Other approaches that aim at learning the parameters of an underlying model have also been explored. For example Ponsen and Spronck \cite{GA} used evolutionary learning techniques, but face the same problem of dimensionality. The difficulty to work with multi-scale goals and plans is handled directly by case-based reasoning (CBR), which has been adapted for units behavior with continuous action models \cite{Molineaux08}, an integrated RL/CBR algorithm using continuous models, or with hybrid CBR/RL transfer learning \cite{CBR-RL}. Reactive planning \cite{WeberCig10}, a decompositional planning similar to hierarchical task networks \cite{HTNPlanning}, allows for plans to be changed at different granularity levels and so for multi-scale (hierarchical) goals integration of low-level control. Synnaeve and Bessi\`{e}re \cite{SynnaeveMicroCig11} achieve hierarchical goals (coming from tactical decisions) integration through the addition of another sensory input corresponding to the goal's objective.

>>>>

% MACHINE LEARNING:
Concerning machine learning-based approaches, Weber and Mateas \cite{WeberCig09} proposed ``a data mining approach to strategy prediction'' and performed supervised learning (from buildings features) on labeled StarCraft replays. Dereszynski et al. \cite{HMMstrat_RTS_AIIDE11} used HMM to learn the transition probabilities of sequences of constructions and kept the most probables to produce probabilistic behavior models (in StarCraft). Synnaeve and Bessi\`{e}re \cite{SynnaeveOpeningCig11} used the dataset of \cite{WeberCig09} and presented a Bayesian semi-supervised model to learn from replays and predict openings (early game strategies) from StarCraft replays. The openings are labeled by EM clustering considering appropriate features. Then, in \cite{SynnaeveAIIDE11}, they presented an unsupervised learning Bayesian model for tech-tree prediction, still using replays. % Finally \cite{GemineImitative} used the same ``build-order features'' approach to learn to adapt the bot's build order to the opponents strategy in StarCraft 2.

@@

% MACHINE LEARNING:
Concerning tactical decision making, many different approaches have been explored such as machine learning or game tree search. Concerning machine learning approaches, 
Hladky and Bulitko \cite{Hladky2008} benchmarked hidden semi-Markov models (HSMM) and particle filters in first person shooter games (FPS) units tracking. They showed that the accuracy of occupancy maps was improved using movement models (learned from the player behavior) in HSMM. Kabanza et al. \cite{OBRecog} improve the probabilistic hostile agent task tracker (PHATT \cite{PHATT}, a simulated HMM for plan recognition) by encoding strategies as HTN, used for plan and intent recognition to find tactical opportunities. Sharma et al. \cite{CBR-RL} combined CBR and reinforcement learning to enable reuse of tactical plan components. Cadena and Garrido \cite{CadenaG11} used fuzzy CBR (fuzzy case matching) for strategic and tactical planning. Finally, \cite{SynnaeveTactics} combined space abstraction into regions from \cite{Perkins10} and tactical-decision making by assigning scores (economical, defenses, etc.) to regions and looking for their correspondences to tactical moves (attacks) in pro-gamers replays.

@@

% Machine learning:
There has been a significant amount of work on using machine learning techniques for the problem of reactive control. Bayesian modeling has been applied to inverse fusion of the sensory inputs of the units \cite{SynnaeveMicroCig11}, which subsumes potential fields, allowing for integration of tactical goals directly in micro-management.

Additionally, there has been some interesting uses of reinforcement learning (RL) \cite{Sutton}: 
%\cite{WenderRL} evaluated the different major RL algorithms for (decentralized) micro-management, which perform all equally.
Marthi et al. \cite{Marthi05} employ concurrent hierarchical Q-learning (units Q-functions are combined at the group level) RL to efficiently control units in a ``one robot with multiple effectors'' fashion. Madeira et al. \cite{Madeira06} advocate the use of prior domain knowledge to allow faster RL learning and applied their work on a turn-based strategy game. In real game setups, the actions spaces to explore is gigantic, it requires to use the structure of the game in a partial program (or a partial Markov decision process) and a shape function (or a heuristic) \cite{Marthi05}. Evolutionary optimization by simulating fights can easily adapted to any parameter-dependent micro-management control model, as shown by \cite{OthmanSimu} which optimizes an AIIDE 2010 micro-management competition bot.

Other approaches that aim at learning the parameters of an underlying model have also been explored. For example Ponsen and Spronck \cite{GA} used evolutionary learning techniques, but face the same problem of dimensionality. The difficulty to work with multi-scale goals and plans is handled directly by case-based reasoning (CBR), which has been adapted for units behavior with continuous action models \cite{Molineaux08}, an integrated RL/CBR algorithm using continuous models, or with hybrid CBR/RL transfer learning \cite{CBR-RL}. Reactive planning \cite{WeberCig10}, a decompositional planning similar to hierarchical task networks \cite{HTNPlanning}, allows for plans to be changed at different granularity levels and so for multi-scale (hierarchical) goals integration of low-level control. Synnaeve and Bessi\`{e}re \cite{SynnaeveMicroCig11} achieve hierarchical goals (coming from tactical decisions) integration through the addition of another sensory input corresponding to the goal's objective.
